Real-time resolution of short-read assembly graph using ONT long reads

### 2020-11-23 paper_edit.tex
add supporting info legends

\end{thebibliography}
\end{document}

>>>>

\end{thebibliography}

\clearpage
\section*{\review{Supporting information}}

\paragraph*{\review{Fig S1}}
\review{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}. Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs. On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.}

\paragraph*{\review{Fig S2}}
\review{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}

\paragraph*{\review{Table S1}}
\review{Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}

\end{document}
